Spatiotemporal models of `r paste(params$species)` biomass with AR1

### 2020-11-25 analysis/SOPO/2-trawl-depth-only-model.Rmd
minor housekeeping

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    # species: "Redbanded Rockfish"
    # species: "North Pacific Spiny Dogfish"
    # species: "Pacific Ocean Perch"
    # species: "Big Skate"
    species: "Pacific Cod"
    #species: "Petrale Sole"
    #species: "Widow Rockfish"
    # species: "Bocaccio"
    # region: "All synoptic surveys"
    region: "Both odd year surveys"
    knots: 300
    covariates: "" # +as.factor(ssid)
    #additional fixed-effect covariates
    #covs: "-ssid-only" # covariate string used to name model rds 
    covs: "-tv-depth-only"
    #covs: "-trawled-ssid"
    AR1: FALSE
    fixed_spatial: TRUE
    update_model: FALSE # TRUE
    update_model_check: FALSE # TRUE
    update_predictions: FALSE # TRUE
    update_index: FALSE # TRUE
---

>>>>

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    # species: "Redbanded Rockfish"
    # species: "North Pacific Spiny Dogfish"
    # species: "Pacific Ocean Perch"
    # species: "Big Skate"
    species: "Pacific Cod"
    #species: "Petrale Sole"
    #species: "Widow Rockfish"
    # species: "Bocaccio"
    # region: "All synoptic surveys"
    region: "Both odd year surveys"
    knots: 300
    covariates: "" # +as.factor(ssid)
    #additional fixed-effect covariates
    #covs: "-ssid-only" # covariate string used to name model rds 
    covs: "-tv-depth-only"
    #covs: "-trawled-ssid"
    AR1: FALSE
    fixed_spatial: TRUE
    update_model: FALSE # TRUE
    update_model_check: FALSE # TRUE
    update_predictions: FALSE # TRUE
    update_index: FALSE # TRUE
---

### 2020-11-25 analysis/SOPO/2-trawl-no-covs-model.Rmd
minor housekeeping

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params:
    # species: "Redbanded Rockfish"
    species: "North Pacific Spiny Dogfish"
    # species: "Pacific Ocean Perch"
    # species: "Bocaccio"
    # species: "Yelloweye Rockfish"
    # species: "Pacific Sand Lance"
    # species: "Pacific Herring"
    # region: "All synoptic surveys"
    region: "Both odd year surveys"
    start_year: 2003
    knots: 300
    covariates: "" # +as.factor(ssid)
    #additional fixed-effect covariates
    covs: "-no-covs-300" # covariate string used to name model rds
    AR1: TRUE
    fixed_spatial: FALSE
    update_model: FALSE
    update_model_check: FALSE #TRUE
    update_predictions: FALSE #TRUE
    update_index: FALSE
---

>>>>

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with AR1"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params:
    # species: "Redbanded Rockfish"
    species: "North Pacific Spiny Dogfish"
    # species: "Pacific Ocean Perch"
    # species: "Bocaccio"
    # species: "Yelloweye Rockfish"
    # species: "Pacific Sand Lance"
    # species: "Pacific Herring"
    # region: "All synoptic surveys"
    region: "Both odd year surveys"
    start_year: 2003
    knots: 300
    covariates: "" # +as.factor(ssid)
    #additional fixed-effect covariates
    covs: "-no-covs-300" # covariate string used to name model rds
    AR1: TRUE
    fixed_spatial: FALSE
    update_model: FALSE
    update_model_check: FALSE #TRUE
    update_predictions: FALSE #TRUE
    update_index: FALSE
---
